%!TeX program=xelatex
\documentclass[10pt, letterpaper]{article}

% refresh version information and import VC macros
\immediate\write18{sh ./vc}
\input{./vc}

\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{letterpaper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage[usenames,dvipsnames]{xcolor} % fontspec loads color
\defaultfontfeatures{Mapping=tex-text}
% \setmainfont{URW Bookman}
\setromanfont[Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
\setmonofont[Scale=1.0]{Latin Modern Mono}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}

% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\small #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{2em}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\large} 
\subsubsectionfont{\mdseries\upshape\normalsize} 

% revision info in the page footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[RF]{\textcolor{gray}{\footnotesize Rev. \VCRevision\\\GITAuthorDate}}
\fancyfoot[CF]{\thepage}
\renewcommand{\headrulewidth}{0pt}
% also, add \thispagestyle after \maketitle to override class prescription 

% BIB
\usepackage[backend=biber,style=authortitle,maxnames=30,sorting=ydnt,dashed=false]{biblatex}

\addbibresource{personal.bib}

% PDF SETUP
\usepackage[bookmarks, colorlinks, breaklinks, 
	pdftitle={Giovanni Luca Ciampaglia - vita},
	pdfauthor={Giovanni Luca Ciampaglia},
	pdfproducer={http://glciampaglia.com/}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

%\nocite{*}

% DOCUMENT
\begin{document}
{\LARGE Giovanni Luca Ciampaglia}\\\textcolor{gray}{\emph{(Joh-vah-nee Loo-kah Chahm-pa-yaa)}}\\[.75cm]
4130 Campus Drive\\
Hornbake Library South, room 2117C\\
College Park, MD 20742-4345\\
Phone: \texttt{+1 (301)\,405-2768}\\[.2cm]
Email: \href{mailto:gciampag3@umd.edu}{gciampag@umd.edu}\\
Homepage: \href{http://www.glciampaglia.com/}{glciampaglia.com}\\[.2cm]
ORCiD: \href{https://orcid.org/0000-0001-5354-9257}{0000-0001-5354-9257}\\
Github: \href{http://github.com/glciampaglia}{github.com/glciampaglia}\\ 
LinkedIn: \href{http://linkedin.com/in/giovanni-luca-ciampaglia}{linkedin.com/in/giovanni-luca-ciampaglia}\\
Scholar: \href{https://scholar.google.com/citations?user=ay9uGpcAAAAJ}{scholar.google.com/citations?user=ay9uGpcAAAAJ}\\
% Gender: Male
% Born:  July 12, 1980\\
% Nationality: Italian (J1 visa, Two-Year rule waiver pending)

\section*{Current Affiliation}

College of Information Studies\\
University of Maryland

\section*{Research Interests}
Data Science • Computational Social Science • Network Science

%\section*{Competences}
%Modeling • Big data • Simulation

\section*{Education}
\noindent

\years{2012}\textbf{Ph.D. in Informatics\textsuperscript{\textasteriskcentered}}\\
%
\textsl{Università della Svizzera Italiana}, Lugano, Switzerland\\
%
\textsc{Supervisors}: Luca Gambardella (IDSIA), Alberto Vancheri (SUPSI), Paolo
Giordano (TU Wien)\\
\textasteriskcentered~\emph{\footnotesize U.S. equivalent degree: Computer Science.}\\

\years{2006}\textbf{\textsl{Laurea} in Computer Science (M.Sc. equivalent)}\\ 
%
Sapienza University, Rome, Italy\\
%
\textsc{Supervisor}: Brunello Tirozzi

% \years{1999}\textbf{\textsl{Maturità Scientifica}}\\
% %
% \textsl{Liceo Scientifico Isacco Newton}, Rome, Italy

\section*{Research}

\years{2022-present}\textbf{University of Maryland} (College Park, MD, USA)\\
%
Assistant Professor\\
%
College of Information Studies\\

\years{2018-2022}\textbf{University of South Florida} (Tampa, FL, USA)\\
%
Assistant Professor\\
%
College of Engineering, Department of Computer Science and Engineering\\

\years{2015-2018}\textbf{Indiana University} (Bloomington, IN, USA)\\
%
Assistant Research Scientist\\
%
Indiana University Network Science Institute\\

\years{2013-2015}\textbf{Indiana University (Bloomington, IN, USA)}\\
%
Postdoctoral fellow\\
%
Center for Complex Networks and Systems Research (Prof. Filippo Menczer)\\

\years{Jul.-Aug. 2011}\textbf{Wikimedia Foundation, Inc. (San Francisco, CA, USA)}\\
%
Research intern\\
%
Wikimedia Summer of Research, Community Department (Dr. Diederik Van Liere)\\

\years{2010-2011}\textbf{Swiss Federal Institute of Technology (Zürich, Switzerland)}\\ 
%
Research associate\\
%
Chair of Sociology, in particular Modeling and Simulation (Prof. Dirk Helbing)

\section*{Teaching}

\years{2019}\textbf{University of South Florida (Tampa, FL, USA)}\\
%
College of Engineering\\
%
\emph{COP 2513 Intro to Object Oriented Programming for IT}\\

\years{2018-present}\textbf{University of South Florida (Tampa, FL, USA)}\\
%
College of Engineering\\
%
\emph{CIS4930/6930 Special Topics ``Social Media Mining''}\\

\years{2015}\textbf{Indiana University (Bloomington, IN, USA)}\\
%
School of Informatics and Computing\\
%
\emph{I690 Mathematical Modeling of Complex Systems: Introduction to Game
Theory} (guest lecturer)\\

\years{2013}\textbf{Indiana University (Bloomington, IN, USA)}\\
%
School of Informatics and Computing\\
%
\emph{I690 Mathematical Modeling of Complex Systems: Agent-based models} (guest lecturer)\\

\years{2010-2011}\textbf{Swiss Federal Institute of Technology  (Zürich,
Switzerland)}\\ 
%
Department of Humanities, Social and Political Sciences\\
%
\emph{Lectures with Computer Exercises: Modelling and Simulating Social Systems with \textsc{matlab}}\\ 

\years{2007-2008}\textbf{\textsl{Università della Svizzera Italiana} (Lugano,
Switzerland)}\\
%
Faculty of Informatics\\ 
%
\emph{Artificial Intelligence and Knowledge Management} (T.A. for Prof. Luca Maria
Gambardella)\\ 
%
\emph{Computer Networking} (T.A. for Prof. Antonio Carzaniga)

\section*{Industry}

\years{2012-2013}\textbf{Wikimedia Foundation, Inc. (San Francisco, CA, USA)}\\
%
Research Analyst\\
%
Technology Department, (Dr. Dario Taraborelli)

\section*{Publications}

\input{sectionbiblio}

\section*{Funding}

\years{2023} \textsc{National Science Foundation}. National AI Research Institutes, Senior Personnel. \$20,000,000.\\
%
\years{2023} \textsc{Social Science Research Council}, Mercury Project, Co-PI.
\$228,980.\\
%
\years{2023} \textsc{National Science Foundation}. CAREER, PI. \$603,502.\\
%
\years{2019} \textsc{National Science Foundation}. SaTC-SBE EAGER, PI. \$312,505.\\
%
\years{2018} \textsc{Craig Newmark Philantropies}. Co-PI. \$70,786.\\
%
\years{2017} \textsc{Democracy Fund}. Prototype fund, Co-PI. \$50,000.\\
%
\years{2016} \textsc{Indiana University}. OVPR Collaborative Research and
Creative Activities Fund, PI. \$20,000.\\
%
\years{2012} \textsc{Swiss National Science Foundation}. Postdoctoral
fellowship. \$63,450.\\
%
\years{2011} \textsc{Singapore Management University}. Travel grant, SocInfo
2011. \$1,358.\\
%
% \years{2010}\textsc{Visiting studentship} (3 months) ETH Zürich,
% Switzerland.\\ % \years{2008}\textsc{Admission to summer school} (1 month)
% Santa Fe Institute Complex Systems Summer School.\\ %
% \years{2006}\textsc{Doctoral studentship} (4 years) Swiss National Science
% Foundation.
  
%\section*{Presentations \& Outreach}

%\years{2017} \textsc{ICDM 2017}, Tutorial on ``Mining Misiformation in Social Media'', \emph{Scheduled} (acceptance rate 3/15).\\
%%
%\years{2017} \textsc{Journalism Interactive}, College Park, MD. October 21. Invited
%talk.\\
%%
%\years{2017} \textsc{The Skyline Club}. Indianapolis, IN. September 28. Invited talk.\\
%%
%\years{2017} \textsc{National Endowmnent for Democracy}. Washington, DC. September 26. Invited talk.\\
%%
%\years{2017} \textsc{Johannes Gutenberg University}, Germany. June 28.
%Keynote talk (host Prof. Olga Troitschanskaia).\\
%%
%\years{2017} \textsc{Max Plank Institute for Software Systems}, Germany. June 26. Invited talk (host Prof. Krishna Gummadi).\\
%%
%\years{2017} \textsc{NetSci 2017}, satellite workshop ``Social Influence''. June 19. Invited talk.\\
%%
%\years{2017} \textsc{ISI Foundation}, Italy. June 8. Invited talk (host Dr. Ciro Cattuto).\\
%%
%\years{2017} \textsc{TTI/Vanguard} ``Hyperconnected'', Boston, MA. April 12. Invited talk.\\
%%
%\years{2017} \textsc{Hariri Institute for Computing, Boston University}. DSI Colloquium. April 26. Invited Talk (host Prof. Azer Bestavros).\\
%%
%\years{2017} \textsc{Boston University}. April 24. Invited talk (host Prof. James Katz).\\
%%
%\years{2017} \textsc{43rd Asilomar Microcomputer Workshop}. April 19. Invited talk.\\
%%
%\years{2017} \textsc{The Matt Townsend Show} (BYU Radio.) March 29. Radio interview [\textsc{\href{https://www.byuradio.org/episode/23aa873d-7d9c-4480-8618-3ef49a9d5041/the-matt-townsend-show-fake-news-don-t-trust-your-gut-mediterranean-diet}{url}}.]\\
%%
%\years{2017} \textsc{Bloomington Press Club}. March 27. Invited talk.\\
%%
%\years{2017} \textsc{American Physical Society}, March Meeting. March 16. Invited talk (host Prof. Guido Caldarelli).\\
%%
%\years{2017} \textsc{Indiana University-Purdue University Indianapolis}. February 23. Invited talk.\\
%%
%\years{2017} \textsc{University of Iowa}. February 20. Invited talk.\\
%%
%\years{2017} \textsc{University of California Davis}. January 20. Invited talk.\\
%%
%\years{2017} \textsc{Tenth ACM Conference on Web Science and Data Mining}. February 10. Poster presentation.\\
%%
%\years{2017} \textsc{Oxford Internet Institute}, University of Oxford. February 9. Invited talk.\\
%%
%\years{2016} \textsc{Noon Edition} (WFIU.). December 2. Radio interview [\textsc{\href{http://indianapublicmedia.org/noonedition/media-consumers-guide-fake-news/}{url}}.]\\
%%
%\years{2016} \textsc{22nd ACM SIGKDD Conference on Knowledge Discovery and Data Mining}, workshop on ``Machine learning meets fashion''. August 16. Poster presentation.\\
%%
%\years{2016} \textsc{Wikimedia Research Showcase}. San Francisco, August 17. Invited talk.\\
%%
%\years{2016} \textsc{DeWitt Wallance Center for Media and Democacry}, Duke University. March 31. Invited talk.\\
%%
%\years{2016} \textsc{Institute for Pure and Applied Mathematics}, UCLA. May 13. Poster presentation.\\
%%
%\years{2015} \textsc{TTI/Vanguard} ``Collaboration and the Future of the Workplace''. October 30. Invited talk.\\
%%
%\years{2015} \textsc{Conference on Complex Systems} (CCS'15). September 28. Oral
%presentation.\\
%%
%\years{2015} \textsc{International Conference on Network Science} (NetSci'15). June 4. Oral presentation.\\
%%
%\years{2015} \textsc{ACM Conference on Computer-Supported Cooperative Work and Social Computing} (CSCW'15). March 16. Oral presentation.\\
%%
%\years{2015} \textsc{ACM Conference on Computer-Supported Cooperative Work and Social Computing} (CSCW'15) workshop on ``Advancing an industry/academic partnership model for Open Collaboration research''. Vancouver, BC, Canada. March 14. Invited talk.\\
%%
%\years{2015} \textsc{GESIS -- Leibniz Institute for the Social Sciences}. March 5. Invited
%talk.\\
%%
%\years{2015} \textsc{University of Cambridge}, Center for Research in the Arts, Social Sciences, and Humanities, March 3rd. Invited talk.\\
%%
%\years{2014} \textsc{Ostrom Workshop Fall Colloquium}, Indiana University, December 1st. Oral presentation.\\
%%
%\years{2014} \textsc{Network Science Colloquium}, Indiana University, October 13. Oral presentation.\\
%%
%\years{2014} \textsc{10th European Conference on Complex Systems} (ECCS14), IMT Lucca, September 22. Oral presentation.\\
%%
%\years{2014} \textsc{Wikimedia Research Showcase}, June 18. Invited talk.\\
%%
%\years{2012} \textsc{3rd Intl Conference on Social Informatics}, Singapore Management University, October 6-8. Oral presentation.\\
%%
%\years{2010} \textsc{4th Intl AAAI Conference on Weblogs and Social Media}, George
%Washington University, May 23-26. Poster presentation.\\
%%
%\years{2009} \textsc{Intl Workshop on Coping with Crises in Complex Socio-Economic
%Systems}, ETH Z\"urich, June 8-12. Oral presentation.\\
%%
%\years{2009} \textsc{USI-UZH p2p Workshop}, \textsl{Università della Svizzera Italiana}, June 17. Oral presentation.\\

\section*{Awards}

\years{2012}\textsc{Best Interactive Visualization} KANTAR “Information is
Beautiful” Awards.\\
%

\section*{Service}

\years{2021} \textsc{National Academies of Science, Engineering, and Medicine}: Ad-hoc Committee on Addressing Inaccurate and Misleading Information about Biological Threats through Scientific Collaboration and Communication.\\
%
\years{2021} \textsc{Board of Trustees}: Conference of Trust and Truth
Online.\\
%
% \years{2021} \textsc{Ad Hoc Committee Member}: National Academic of Science,
% Engineering and Medicine (\emph{to be announced}).\\
% %
\years{2020} \textsc{Academic Liaison}: Conference for Trust and Truth
Online.\\
%
\years{2020} \textsc{Senior PC}: The Web Conference 2020.\\
%
\years{2020} \textsc{Panel Reviewer}: National Science Foundation (SaTC-SBE).\\
%
\years{2019} \textsc{External Reviewer}: French National Research Agency (ANR),
Dutch Research Council (NWO)\\
%
\years{2019} \textsc{Referee}: ACM CSUR, Communications Physics, Europhysics
Letters, Conference for Truth and Trust Online, Europhysics Letters\\
%
\years{2018} \textsc{External Reviewer}: Swiss National Science Foundation,
Rita Allen Foundation.\\
%
\years{2018} \textsc{Program co-chair}: WWW 2018 Alternate track on
``Journalism, Misinformation, and Fact Checking''.\\
%
\years{2017} \textsc{Program co-chair}: SocInfo 2017.\\
%
\years{2017} \textsc{Sponsorship co-chair}: NetSci 2017 (amount raised
\$36,500).\\
%
\years{2017} \textsc{Associate editor}: Journal of Computational Social
Science, Springer.\\
%
\years{2017} \textsc{Co-organizer}: ICWSM 2017 workshop on Digital
Misinformation.\\
%
\years{2016} \textsc{Co-organizer}: Open Science for an Open Society, satellite
workshop at the Conference on Complex Systems (2016).\\
%
% \textsc{Member}: Association for Computing Machinery.\\ % \years{2015}
% \textsc{Advisory board member}: Open Collaboration Data Factory (NSF Grant
% 144920).\\ %
\years{2014-present} \textsc{Co-organizer}: Computational Social Science,
satellite workshop at the Conference on Complex Systems (2014, 15, 16).\\
%
% \years{2014-present} \textsc{Member}: SIGWEB.\\ % \years{2014-present}
% \textsc{Member}: Complex Systems Society.\\ %
\years{2014} \textsc{Publicity chair}: ACM Web Science 2014.\\
%
\years{2013-2014} \textsc{Guest editor}: EPJ Data Science.\\
%
\years{2013} \textsc{Co-organizer}: Collective Behaviors and Networks,
satellite workshop at ECCS'13.\\
%
\years{2012-present} \textsc{Reviewer}: Journal of the Royal Society:
Interface, CACM, Scientific Reports, ACM TOIT, Network Science, Frontiers in
ICT, PeerJ Computer Science, CSCW (\emph{distinguished reviewer}), Entropy, EPJ
Data Science, Adv. Comp. Sys., JASSS, ACM TOIS, IEEE Internet Computing, IEEE
TKDE, PLoS ONE, Wikimedia Research Newsletter.\\ 
%
\years{2014-present} \textsc{PC Member}: WWW (2017),
\href{http://www.snow-workshop.org/}{SNOW} (2014, 2016), CompleNet (2016),
\href{http://cnets.indiana.edu/cool2014/}{COOL}, CRIMENET (2014), DataWiz
(2014), \href{http://dyad.di.unito.it/}{DYAD} (2014), HyperText (2015), SocInfo
(2014, 2016).\\

%\section*{IT \& programming}

%Programming languages: C, Java, MATLAB.\\
%%
%Scripting languages: Javascript, Python/Cython, Unix Shell, VIM.\\
%%
%Parallel Computing: PBS, IPython, OpenMP, MPI, PIG, Hive.\\
%%
%Statistical analysis: R, SciPy + NumPy.\\
%%
%Network analysis: graph-tool, NetworkX, Gephi.\\
%%
%Database systems: MySQL, SQLite.\\
%%
%Web Frameworks: Django, jQuery.\\
%%
%Revision control: Git.\\
%%
%Digital typography: \LaTeX, \XeTeX.\\
%%
%Personal productivity system: GTD.

%\section*{Languages}

%Italian (native speaker)\\
%%
%English (professional proficiency)\\
%%
%German (basic proficiency)\\
%%
%French (basic proficiency)

%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in {\fontspec{Latin Modern Mono} \XeTeX}\\
\href{http://glciampaglia.com}{http://glciampaglia.com}}
\end{center}

\end{document}
