\documentclass[10pt, a4paper]{article}
\usepackage{fontspec} 
\usepackage{lipsum}

% DOCUMENT LAYOUT
\pagestyle{empty}
\usepackage{geometry} 
\geometry{
    a4paper, 
    textwidth=5.5in,
    textheight=8.5in,
    marginparsep=7pt, 
    marginparwidth=.6in
}
\setlength{\parskip}{1em}
\setlength{\parindent}{1em}

% FONTS
\usepackage[usenames,dvipsnames]{color}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
\setmonofont[Scale=1.0]{LMMono10}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[dvipdfm, bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Giovanni Luca Ciampaglia - cover letter},
	pdfauthor={Giovanni Luca Ciampaglia},
	pdfproducer={http://www.inf.usi.ch/phd/ciampaglia/}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

\begin{document}

% SENDER ADDRESS 
\center
\textsc{Giovanni Luca Ciampaglia\\
Bertastraße 36\\
\oldstylenums{8003} Zürich, Switzerland\\
+41 79 718 81 57\\
\href{mailto:ciampagg@usi.ch}{ciampagg@usi.ch}
}

\raggedright
\vspace{0.5in}
\today\\[2em]

% RECIPIENT ADDRESS
Bryony Jones\\
Wikimedia Foundation Inc.\\
149 New Montgomery Street, 3rd Floor\\
San Francisco, CA 94105\\
USA\\
\vspace{2em}

% TEXT -- ADD YOUR LETTER HERE
Dear Bryony:

I would like to apply for the summer fellowship at the community department of
the Wikimedia Foundation. My background is in computer science and I am working
on social informatics research at the University of Lugano, Switzerland. In my
doctoral dissertation I propose a model of commons-based peer production and
with it I study the conditions for the existence of different levels of user
participation.

I have a solid knowledge of Python and its scientific libraries and a good
experience of large-scale data analysis tasks on Mediawiki database dumps from
the English Wikipedia. I also recently developed an interactive web application
using technologies such as Django and jQuery.

I think that my research has the potentials for helping the Foundation in its
core mission of making Wikipedia and her sibling projects a long-term,
sustainable effort for the dissemination of human knowledge, and in providing a
viable alternative to classical organizational structures.

Besides my CV, enclosed within this application you will find: an excerpt of 10
pages with the introduction from my doctoral dissertation proposal, which was
accepted by my doctoral committee last June; two of my recent academic
publications; the latest draft of a chapter from my doctoral dissertation.

Due to time constraints with my thesis, my availability for the fellowship
would be for the month of August and possibly with part of July.

% SIGNATURE -- PUT YOUR NAME IN EMPH 
\vspace{2em}
\raggedleft
With my best regards,\\
\emph{Giovanni Luca Ciampaglia}\\[1em]
\vfill
\raggedright
Enclosed:\\[.1cm]
\footnotesize
\texttt{curriculum\_glc.pdf}\\
\texttt{phdproposal\_excerpt.pdf}\\
\texttt{icwsm2010\_full.pdf}\\
\texttt{saso2010.pdf}\\ 
\texttt{gsa\_draft.pdf}


\end{document}
