% :vim:let g:TexCompileRule_pdf='xelatex -interactionmode=nonstop $*'
\documentclass[10pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{color}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
\setmonofont[Scale=1.0]{LMMono10}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[dvipdfm, bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Giovanni Luca Ciampaglia - vita},
	pdfauthor={Giovanni Luca Ciampaglia},
	pdfproducer={http://www.inf.usi.ch/phd/ciampaglia/}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Giovanni Luca Ciampaglia}\\[1cm]
Bertastraße 36 / 8003 Zürich / Switzerland\\[.2cm]
Phone: \texttt{+41 43 817 20 75}\\
Mobile: \texttt{+41 79 718 81 57}\\
Email: \href{mailto:ciampagg@usi.ch}{ciampagg@usi.ch}\\
\textsc{url}: \href{http://www.inf.usi.ch/phd/ciampaglia/}{http://www.inf.usi.ch/phd/ciampaglia/}\\[.2cm]
Gender: Male\\
Born:  July 12, 1980\\
Nationality: Italian\\
Swiss Residence Permit: Type B (valid for employment)

\section*{Areas of specialization}
Social Informatics • Computational Social Sciences

\section*{Areas of competence}
Agent-based modeling • Large-scale data analysis • Simulation

\section*{Education}
\noindent
\years{2011}\textbf{Ph.D. candidate in Informatics (Expected: December 15, 2011)}\\
Università della Svizzera Italiana, Lugano, Switzerland\\
\textsc{Supervisor}: Luca Maria Gambardella (IDSIA)\\[.1cm]
\years{2006}\textbf{Laurea in Computer science (BSc + MSc equivalent)}\\
Sapienza -- University of Rome, Rome, Italy\\
\textsc{Supervisor}: Brunello Tirozzi (La Sapienza)\\[.1cm]
\years{2000}\textbf{Maturità Scientifica (Secondary Education)}\\
Liceo Scientifico Isacco Newton, Rome, Italy\\[.1cm]

\section*{Appointments held}
\subsection*{Research}
\years{2011}\textbf{Wikimedia Foundation, Inc. (San Francisco, USA)}\\
Research fellow\\
Wikimedia Summer of Research, Community Department (Diederik Van Liere)\\[.1cm]

\years{2011}\textbf{ETH Zürich (Switzerland)}\\
Research associate\\
Chair of Sociology, in particular Modeling and Simulation (Prof. Dirk
Helbing)\\[.1cm]

\subsection*{Teaching}
\years{2010}\textbf{ETH Zürich (Switzerland)}\\
Lecturer\\
\emph{Lecture with Computer Exercises: Modelling and Simulating Social Systems with \textsc{matlab}} (30 h)\\[.1cm]
\years{2008}\textbf{Università della Svizzera Italiana (Lugano, Switzerland)}\\
Teaching assistant\\
\emph{Artificial Intelligence and Knowledge Management} (18 h)\\[.1cm]
\years{2007}\textbf{Università della Svizzera Italiana (Lugano, Switzerland)}\\
Teaching assistant\\
\emph{Computer Networking} (18 h)\\[.1cm]

\section*{Grants \& awards}
\years{2010}\textsc{Visiting studentship} (3 months) ETH Zürich, Switzerland\\
%
\years{2008}\textsc{Admission to summer school} (1 month) SFI Complex Systems
Summer School, Santa Fe, USA.\\
%
\years{2006}\textsc{Doctoral studentship} (4 years) Swiss National Science
Foundation\\

\section*{IT \& programming}
Programming languages: C, Java, MATLAB\\
Scripting languages: Javascript, Python (SciPy + NumPy, Cython), PHP, Bash, ZSH\\
Markup languages: XHTML, CSS, XML\\
Database systems: MySQL, PostgreSQL, SQLite, MongoDB\\
Web Frameworks: Django, jQuery\\
Revision control: Darcs, SVN, Git\\
Digital typography: \LaTeX, \XeTeX\\
Batch systems: PBS\\
Favorite editor: Vim\\
Personal productivity system: GTD\textsuperscript{®}

\section*{Languages}
Italian (native speaker)\\
English (professional proficiency)\\
French (basic proficiency)

\section*{Publications \& talks}

\subsection*{Peer-reviewed conference papers}
\noindent
\years{2011} ``A bounded confidence approach to understanding user participation
in peer production systems'', \emph{Lecture Notes in Computer Science} Vol.
6984, pp. 269--282. \doi{http://dx.doi.org/10.1007/978-3-642-24704-0\_29}\\
%
\years{2010b} ``Beyond notability. Collective deliberation on content inclusion
in Wikipedia'', (with Dario Taraborelli) \emph{Fourth IEEE intl conf. on
self-adaptive and self-organizing systems workshops} September 27-28 2010,
Budapest, Hungary. \doi{http://dx.doi.org/10.1109/SASOW.2010.26}\\
%
\years{2010a} ``Empirical analysis of user participation in Online communities:
the case of Wikipedia'', (with Alberto Vancheri) \emph{Fourth intl AAAI conf. on
weblogs and social Media}, May 23-26 2010, Washington D.C., USA.
\pdf{http://www.aaai.org/ocs/index.php/ICWSM/ICWSM10/paper/download/1517/1861}\\
%
\years{2008} ``Go east: a residential land use model for the periphery of
Rome'', (with B. Tirozzi) \emph{Intl cong. on environmental modelling and
software}, July 7-10, 2008, Barcelona, Spain.
\pdf{http://www.inf.usi.ch/phd/ciampaglia/papers/RomeModel2008.pdf}\\
%
\years{2007} ``An ant colony verification algorithm'', (with Rachid Rebiha)
\emph{Intl conf. on intelligent systems design and applications}, October 22-24
2007, Rio de Janeiro, Brazil.
\pdf{http://www.inf.usi.ch/phd/ciampaglia/papers/RebihaACOVerification07.pdf}\\

\subsection*{Theses \& Working papers}
\noindent
\years{2008} ``The cost of strategic adaptation in a simple conceptual model of
climate change.'' (with A. Millner, N. Aravamudan, and J. Foster) Working Paper
for the Santa Fe Institute Complex Systems Summer School.
\pdf{http://www.santafe.edu/events/workshops/images/3/32/Simpleclimatechange.pdf}\\
%
\years{2006} ``Modello di sviluppo urbano mediate automi cellulari e sistemi
multi-agente'', MSc Thesis in Computer Science.\\

%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in {\fontspec{Nimbus Roman No9 L} \XeTeX}\\
\href{http://www.inf.usi.ch/phd/ciampaglia}{http://www.inf.usi.ch/phd/ciampaglia}}
\end{center}

\end{document}
